\normalfont\spacedallcaps{The economic consequences of different attitudes of a policy maker: a combined epidemiological-econometric study}

### 2021-03-22 Manuscript/manuscript.tex
PUB

In all tables the following significance code will be used:  *** for 0.001,  ** for 0.01 and * for 0.05

@@

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ coefficients as obtained by the DID  regression, for sales value data (with the baseline $100=2015$) de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. The values of the intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Info.  
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & -40.16 *** & 2.01  & -19.99 & -60.07 *** & 2.77  & -21.64 & -16.45 *** & 2.77  & -5.92 \\ \hline
{\color[HTML]{009901} Footwear}        & -38.70 *** & 1.73  & -22.35 & -65.78 *** & 2.39  & -27.49 & -20.62 *** & 2.39  & -8.62 \\ \hline
{\color[HTML]{F56B00} Appliances}      & -20.32 *** & 2.50  & -8.11  & -27.34 *** & 3.45  & -7.90  & -3.68  & 3.45  & -1.06  \\ \hline
{\color[HTML]{00009B} Photo-optics}    & -34.14 *** & 2.55  & -13.38 & -52.32 ***  & 3.52  & -14.84 & -7.86 *  & 3.52  & -2.23 \\ \hline
{\color[HTML]{6200C9} Homeware}   & -10.51 *** & 1.50  & -6.98  & -18.99 ***  & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
{\color[HTML]{00D2CB} Household tools} & -13.02  *** & 3.51  & -3.70 & -30.23 *** & 4.85  & -6.23    & 2.33   & 4.85  & 0.48  \\ \hline
{\color[HTML]{FFC9FD} Games}             & -27.55 *** & 3.47 & -7.93 & -64.31 *** &  4.79  & -13.40 & 0.26 &  4.79 & 0.05

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for redundancy funds (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for the different lock-down timings. The values of the  intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Information D. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{343434} Total}        & 706 ***   & 3.8     & 181  & 217  ***  & 3.8     & 55.98 & 144  ***  & 3.88     & 37.07 \\ \hline
{\color[HTML]{343434} Manufacture}  & 494  ***  & 3.4     & 143 & 162  ***  & 3.4     & 46.91    & 111   *** & 3.4     & 32.17  \\ \hline
{\color[HTML]{343434} Trade}        & 16.4  *** & 0.21  & 75.35  & 3.68 ***  & 0.21  & 16.9 & 2.88  *** & 0.21  & 13.27 \\ \hline
{\color[HTML]{343434} Construction} & 134  ***   & 0.54  & 249 & 29  ***   & 0.54  & 54.45 & 14   ***  & 0.54  & 27.28 \\ \hline
\label{CIG_DID}
\end{tabular}
\end{table}
\end{landscape}

@@

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/Selling_Scenario_1_1_1.pdf}
         \caption{Active PM} 
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/Selling_Scenario_1.5_1.5_1.5.pdf}}
         \caption{Lazy PM}
     \end{subfigure}
\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).  These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).  The error bars were calculated by considering the error propagation 
 }
\label{Selling_sector_effects}
\end{figure}

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_effect_1_1_1.pdf}
         \caption{Active PM} 
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_1.5_1.5_1.5.pdf}}
         \caption{Lazy PM}
     \end{subfigure}
\caption{Redundancy funds variation(in terms of hours paid) for the scenarios where an active vs. lazy PM is considered. These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value). The error bars, although they are not clearly visible because they are too reduced,  were calculated by considering the error propagation}
\label{CIG_sector_effects}
\end{figure}

@@

\begin{table}[]
\begin{center}
\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).  These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).  The errors were calculated by considering the error propagation}
\begin{tabular}{l|l|l|l|l}
                & Active & \sigma   & Lazy &  \sigma \\ \hline
Clothing        & -481   & 26 & -45  & 9 \\ \hline
Footwear        & -264   & 23 & -49  & 8 \\ \hline
Appliances      & -242   & 29 & -20  & 2 \\ \hline
Photo-optics    & -410   & 30 & -39  & 3 \\ \hline
Homeware        & -127   & 18 & -14  & 1 \\ \hline
Household tools & -161   & 42 & -22  & 4 \\ \hline
Games           & -342   & 41 & -48  & 3
\label{Selling_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\begin{center}
\caption{Redundancy funds variation(in terms of hours paid) for the scenarios where an active vs. lazy PM is considered. These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value). The errors  were calculated by considering the error propagation.}
\begin{tabular}{l|l|l|l|l}
             & Active &  \sigma  & Lazy &   \sigma  \\ \hline
Total        & 2938   & 38 & 889  & 9.7 \\ \hline
Manufacture  & 2180   & 38 & 648  & 9.7 \\ \hline
Trade        & 52     & 3  & 19   & 0.8 \\ \hline
Construction & 407    & 11 & 135  & 2.8
\label{CIG_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

@@

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ coefficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} for the different lock-down timings where the food selling are modified in order to have,  during the lock-down timings, the same constant value of February.  Note that no significant difference can be found with respect to the coefficient obtained in Tab \ref{selling_DID_table_delta}. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & -39.71 ***  & 2.00  & -19.76 & -59.34 *** & 2.77  & -21.37 & -15.50  *** & 2.77 & -5.58 \\ \hline
{\color[HTML]{009901} Footwear}        & -38.24 *** & 1.73  & -22.08 & -65.05  *** & 2.39  & -27.18 & -19.68 *** & 2.39  & -8.22 \\ \hline
{\color[HTML]{F56B00} Appliances}      & -19.86 *** & 2.50  & -7.93 & -26.61 *** & 3.45  & -7.69  & -2.73 & 3.45  & -0.79 \\ \hline
{\color[HTML]{00009B} Photo-optics}    & -33.68 ***  & 2.55 & -13.21 & -51.59 ***  & 3.52 & -14.64 & -6.91 & 3.52  & -1.96 \\ \hline
{\color[HTML]{6200C9} Homeware}   & -10.06  *** & 1.50  & -6.68  & -18.26 *** & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
{\color[HTML]{00D2CB} Household tools} & -12.57 *** & 3.51 & -3.57 & -29.50 ***  & 4.85  & -6.07   & 3.28   & 4.85  & 0.67  \\ \hline
{\color[HTML]{FFC9FD} Games}             & -27.10 *** & 3.47 & -7.80 & -63.58 *** &  4.79 & -13.24 & 1.21 &  4.79 & 0.25

@@

\begin{table}
\centering
\caption{Clothing}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.33  *** & 0.08  \\ \hline
$\Delta_{T1}$   & -36.33 *** & 2.15  \\ \hline 
$\Delta_{T2}$   & -56.23 *** & 2.77   \\ \hline
$\Delta_{T3}$   & -11.95 *** & 2.86 \\ \hline
\label{ASS_Clothing}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Footwear}
\begin{tabular}{l|l|l}
                & Value  &  $\sigma$ \ \\ \hline
$\Delta$ Slope before T1 & -0.18 * & 0.08  \\ \hline
$\Delta_{T1}$   & -38.70 *** & 1.91   \\ \hline
$\Delta_{T2}$   & -63.21 ***  & 2.47  \\ \hline
$\Delta_{T3}$   & -17.61 *** & 2.54  \\ \hline
\label{ASS_Footwear}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Appliances}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
$\Delta_{T1}$   & -19.21 *** & 3.10   \\ \hline
$\Delta_{T2}$   & -26.23 *** & 4.00  \\ \hline
$\Delta_{T3}$   & -2.37 & 4.12  \\ \hline
\label{ASS_Appliances}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Photo-optics}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.40 ***  & 0.07 \\ \hline
$\Delta_{T1}$   & -29.94 *** & 2.73   \\ \hline
$\Delta_{T2}$   & -48.11 *** & 3.52  \\ \hline
$\Delta_{T3}$   & -2.93 & 3.63 \\ \hline
\label{ASS_Photooptics}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household kids}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.16 ** & 0.04  \\ \hline
$\Delta_{T1}$   & -10.51 *** & 1.55  \\ \hline
$\Delta_{T2}$   & -19.00 *** & 2.14  \\ \hline
$\Delta_{T3}$   & -3.61 & 2.14 \\ \hline
\label{ASS_Household_K}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household tools}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.21 *** & 0.05  \\ \hline
$\Delta_{T1}$   & -13.02 *** & 3.53 \\ \hline
$\Delta_{T2}$   & -30.23 ** & 4.88  \\ \hline
$\Delta_{T3}$   & 2.33 & 4.88 \\ \hline
\label{ASS_Household_T}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Games}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.37 ** & 0.10 \\ \hline
$\Delta_{T1}$   & -27.56 *** & 3.63 \\ \hline
$\Delta_{T2}$   & -64.31 *** & 5.01  \\ \hline
$\Delta_{T3}$   & 0.27 & 5.01\\ \hline
\label{ASS_Games}
\end{tabular}
\end{table}

@@

\begin{landscape}
\begin{table}
\caption{
\begin{flushleft}
$\delta$ cofficients as obtained by the DID  regression, for sales value data de-seasoned,  according to equation \ref{DID-eq} \\ for a placebo timings as showed in Fig.  \ref{DID_selling_placebo}
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
& $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{5} $ & $\sigma_{\delta_{5}$ & t      &  $\delta_{6}$ & $\sigma_{\delta_{6}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & 4.87  & 17.47  & 0.28 & 3.94 & 12.65 & 0.31 & 0.70 & 17.48  & 0.04 \\ \hline
{\color[HTML]{009901} Footwear}        & 5.31 & 18.16 & 0.29 & 5.05  & 13.14 & 0.38 & 2.00  &  18. 16 & 0.11 \\ \hline
{\color[HTML]{F56B00} Appliances}      & 4.64 & 8.66  & 0.54 & 1.14 & 6.26  & 0.18  & -0.81  & 8.66 & -0.09  \\ \hline
{\color[HTML]{00009B} Photo-optics}    & 1.71 & 15.18  & 0.11 & 0.84 & 10.99 & 0.07 & 0.70  & 15.18  & 0.11  \\ \hline
{\color[HTML]{6200C9} Homeware}   & 1.23 & 5.15  & 0.24 & -0.07 & 3.72  & -0.018  & -0.86  & 5.15 & -0.17 \\ \hline
{\color[HTML]{00D2CB} Household tools} & 0.26  & 8.78  & 0.03 & -0.21 & 6.36  & -0.03   & 0.14  & 8.79  & 0.97  \\ \hline
{\color[HTML]{FFC9FD} Games}             & 3.26 & 16.55 & 0.20 & 1.12 &  11.98  & 0.09 & 1.37 &  16.56 & 0.08

@@

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for redundancy funds (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for a placebo timings as showed in Fig.  \ref{DID_subsidies_placebo}
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{4} $ & $\sigma_{\delta_{4}$ & t      &  $\delta_{5}$ & $\sigma_{\delta_{5}$  & t     \\ \hline
{\color[HTML]{343434} Total}        & -48   & 163    &  -0.30  & -47   & 163   & -0.29 & -47  & 163    & -0.29 \\ \hline
{\color[HTML]{343434} Manufacture}  & -34   & 114    &  -0.30  & -35   & 114   & -0.30 & -34  & 114     & -0.30   \\ \hline
{\color[HTML]{343434} Trade}        & -1.2   & 3  & -0.31  & -0.9   & 3.7  & -0.23 & -0.9   & 3.7  & -0.26 \\ \hline
{\color[HTML]{343434} Construction} & -8.3   & 30  &  -0.27 &  -7.4    & 30  & -2.44 & -8.10    & 30 & -2.67 \\ \hline
\label{sub_DID_placebo}
\end{tabular}
\end{table}
\end{landscape}

>>>>

In all tables the following significance code will be used:  *** for 0.001,  ** for 0.01 and * for 0.05. SE stands for Standard Error

@@

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ coefficients as obtained by the DID  regression, for sales value data (with the baseline $100=2015$) de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. The values of the intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Info.  
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ SE_{\delta_{1}}$   & t      & $\delta_{2} $ & $SE_{\delta_{2}$ & t      &  $\delta_{3}$ & $ SE_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & -40.16 *** & 2.01  & -19.99 & -60.07 *** & 2.77  & -21.64 & -16.45 *** & 2.77  & -5.92 \\ \hline
{\color[HTML]{009901} Footwear}        & -38.70 *** & 1.73  & -22.35 & -65.78 *** & 2.39  & -27.49 & -20.62 *** & 2.39  & -8.62 \\ \hline
{\color[HTML]{F56B00} Appliances}      & -20.32 *** & 2.50  & -8.11  & -27.34 *** & 3.45  & -7.90  & -3.68  & 3.45  & -1.06  \\ \hline
{\color[HTML]{00009B} Photo-optics}    & -34.14 *** & 2.55  & -13.38 & -52.32 ***  & 3.52  & -14.84 & -7.86 *  & 3.52  & -2.23 \\ \hline
{\color[HTML]{6200C9} Homeware}   & -10.51 *** & 1.50  & -6.98  & -18.99 ***  & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
{\color[HTML]{00D2CB} Household tools} & -13.02  *** & 3.51  & -3.70 & -30.23 *** & 4.85  & -6.23    & 2.33   & 4.85  & 0.48  \\ \hline
{\color[HTML]{FFC9FD} Games}             & -27.55 *** & 3.47 & -7.93 & -64.31 *** &  4.79  & -13.40 & 0.26 &  4.79 & 0.05

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for redundancy funds (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for the different lock-down timings. The values of the  intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Information D. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ SE_{\delta_{1}}$   & t      & $\delta_{2} $ & $SE_{\delta_{2}$ & t      &  $\delta_{3}$ & $SE_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{343434} Total}        & 706 ***   & 3.8     & 181  & 217  ***  & 3.8     & 55.98 & 144  ***  & 3.88     & 37.07 \\ \hline
{\color[HTML]{343434} Manufacture}  & 494  ***  & 3.4     & 143 & 162  ***  & 3.4     & 46.91    & 111   *** & 3.4     & 32.17  \\ \hline
{\color[HTML]{343434} Trade}        & 16.4  *** & 0.21  & 75.35  & 3.68 ***  & 0.21  & 16.9 & 2.88  *** & 0.21  & 13.27 \\ \hline
{\color[HTML]{343434} Construction} & 134  ***   & 0.54  & 249 & 29  ***   & 0.54  & 54.45 & 14   ***  & 0.54  & 27.28 \\ \hline
\label{CIG_DID}
\end{tabular}
\end{table}
\end{landscape}

@@

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/Selling_Scenario_1_1_1.pdf}
         \caption{Active PM} 
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/Selling_Scenario_1.5_1.5_1.5.pdf}}
         \caption{Lazy PM}
     \end{subfigure}
\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).  These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).  The standard error bars were calculated by considering the error propagation 
 }
\label{Selling_sector_effects}
\end{figure}

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_effect_1_1_1.pdf}
         \caption{Active PM} 
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_1.5_1.5_1.5.pdf}}
         \caption{Lazy PM}
     \end{subfigure}
\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs. lazy PM is considered. These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value). The standard error bars, although they are not clearly visible because they are too reduced,  were calculated by considering the error propagation}
\label{CIG_sector_effects}
\end{figure}

@@

\begin{table}[]
\begin{center}
\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).  These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).  The standard errors were calculated by considering the error propagation}
\begin{tabular}{l|l|l|l|l}
                & Active & SE   & Lazy &  SE \\ \hline
Clothing        & -481   & 26 & -45  & 9 \\ \hline
Footwear        & -264   & 23 & -49  & 8 \\ \hline
Appliances      & -242   & 29 & -20  & 2 \\ \hline
Photo-optics    & -410   & 30 & -39  & 3 \\ \hline
Homeware        & -127   & 18 & -14  & 1 \\ \hline
Household tools & -161   & 42 & -22  & 4 \\ \hline
Games           & -342   & 41 & -48  & 3
\label{Selling_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\begin{center}
\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs. lazy PM is considered. These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value). The standard errors were calculated by considering the error propagation.}
\begin{tabular}{l|l|l|l|l}
             & Active &  SE  & Lazy &   SE  \\ \hline
Total        & 2938   & 38 & 889  & 9.7 \\ \hline
Manufacture  & 2180   & 38 & 648  & 9.7 \\ \hline
Trade        & 52     & 3  & 19   & 0.8 \\ \hline
Construction & 407    & 11 & 135  & 2.8
\label{CIG_sector_effects_TAB}
\end{tabular}
\end{center}
\end{table}

@@

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ coefficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} for the different lock-down timings where the food selling are modified in order to have,  during the lock-down timings, the same constant value of February.  Note that no significant difference can be found with respect to the coefficient obtained in Tab \ref{selling_DID_table_delta}. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ SE_{\delta_{1}}$   & t      & $\delta_{2} $ & $SE_{\delta_{2}$ & t      &  $\delta_{3}$ & $SE_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & -39.71 ***  & 2.00  & -19.76 & -59.34 *** & 2.77  & -21.37 & -15.50  *** & 2.77 & -5.58 \\ \hline
{\color[HTML]{009901} Footwear}        & -38.24 *** & 1.73  & -22.08 & -65.05  *** & 2.39  & -27.18 & -19.68 *** & 2.39  & -8.22 \\ \hline
{\color[HTML]{F56B00} Appliances}      & -19.86 *** & 2.50  & -7.93 & -26.61 *** & 3.45  & -7.69  & -2.73 & 3.45  & -0.79 \\ \hline
{\color[HTML]{00009B} Photo-optics}    & -33.68 ***  & 2.55 & -13.21 & -51.59 ***  & 3.52 & -14.64 & -6.91 & 3.52  & -1.96 \\ \hline
{\color[HTML]{6200C9} Homeware}   & -10.06  *** & 1.50  & -6.68  & -18.26 *** & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
{\color[HTML]{00D2CB} Household tools} & -12.57 *** & 3.51 & -3.57 & -29.50 ***  & 4.85  & -6.07   & 3.28   & 4.85  & 0.67  \\ \hline
{\color[HTML]{FFC9FD} Games}             & -27.10 *** & 3.47 & -7.80 & -63.58 *** &  4.79 & -13.24 & 1.21 &  4.79 & 0.25

@@

\begin{table}
\centering
\caption{Clothing}
\begin{tabular}{l|l|l}
                & Value  & $SE$ \\ \hline
$\Delta$ Slope before T1 & -0.33  *** & 0.08  \\ \hline
$\Delta_{T1}$   & -36.33 *** & 2.15  \\ \hline 
$\Delta_{T2}$   & -56.23 *** & 2.77   \\ \hline
$\Delta_{T3}$   & -11.95 *** & 2.86 \\ \hline
\label{ASS_Clothing}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Footwear}
\begin{tabular}{l|l|l}
                & Value  &  $SE$ \ \\ \hline
$\Delta$ Slope before T1 & -0.18 * & 0.08  \\ \hline
$\Delta_{T1}$   & -38.70 *** & 1.91   \\ \hline
$\Delta_{T2}$   & -63.21 ***  & 2.47  \\ \hline
$\Delta_{T3}$   & -17.61 *** & 2.54  \\ \hline
\label{ASS_Footwear}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Appliances}
\begin{tabular}{l|l|l}
                & Value  & $SE$ \\ \hline
$\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
$\Delta_{T1}$   & -19.21 *** & 3.10   \\ \hline
$\Delta_{T2}$   & -26.23 *** & 4.00  \\ \hline
$\Delta_{T3}$   & -2.37 & 4.12  \\ \hline
\label{ASS_Appliances}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Photo-optics}
\begin{tabular}{l|l|l}
                & Value  & $SE$ \\ \hline
$\Delta$ Slope before T1 & -0.40 ***  & 0.07 \\ \hline
$\Delta_{T1}$   & -29.94 *** & 2.73   \\ \hline
$\Delta_{T2}$   & -48.11 *** & 3.52  \\ \hline
$\Delta_{T3}$   & -2.93 & 3.63 \\ \hline
\label{ASS_Photooptics}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household kids}
\begin{tabular}{l|l|l}
                & Value  & $SE$ \\ \hline
$\Delta$ Slope before T1 & -0.16 ** & 0.04  \\ \hline
$\Delta_{T1}$   & -10.51 *** & 1.55  \\ \hline
$\Delta_{T2}$   & -19.00 *** & 2.14  \\ \hline
$\Delta_{T3}$   & -3.61 & 2.14 \\ \hline
\label{ASS_Household_K}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household tools}
\begin{tabular}{l|l|l}
                & Value  & $SE$ \\ \hline
$\Delta$ Slope before T1 & -0.21 *** & 0.05  \\ \hline
$\Delta_{T1}$   & -13.02 *** & 3.53 \\ \hline
$\Delta_{T2}$   & -30.23 ** & 4.88  \\ \hline
$\Delta_{T3}$   & 2.33 & 4.88 \\ \hline
\label{ASS_Household_T}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Games}
\begin{tabular}{l|l|l}
                & Value  & $SE$ \\ \hline
$\Delta$ Slope before T1 & -0.37 ** & 0.10 \\ \hline
$\Delta_{T1}$   & -27.56 *** & 3.63 \\ \hline
$\Delta_{T2}$   & -64.31 *** & 5.01  \\ \hline
$\Delta_{T3}$   & 0.27 & 5.01\\ \hline
\label{ASS_Games}
\end{tabular}
\end{table}

@@

\begin{landscape}
\begin{table}
\caption{
\begin{flushleft}
$\delta$ cofficients as obtained by the DID  regression, for sales value data de-seasoned,  according to equation \ref{DID-eq} \\ for a placebo timings as showed in Fig.  \ref{DID_selling_placebo}
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
& $\delta_{4} $&   $ SE_{\delta_{4}}$   & t      & $\delta_{5} $ & $SE_{\delta_{5}$ & t      &  $\delta_{6}$ & $SE_{\delta_{6}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & 4.87  & 17.47  & 0.28 & 3.94 & 12.65 & 0.31 & 0.70 & 17.48  & 0.04 \\ \hline
{\color[HTML]{009901} Footwear}        & 5.31 & 18.16 & 0.29 & 5.05  & 13.14 & 0.38 & 2.00  &  18. 16 & 0.11 \\ \hline
{\color[HTML]{F56B00} Appliances}      & 4.64 & 8.66  & 0.54 & 1.14 & 6.26  & 0.18  & -0.81  & 8.66 & -0.09  \\ \hline
{\color[HTML]{00009B} Photo-optics}    & 1.71 & 15.18  & 0.11 & 0.84 & 10.99 & 0.07 & 0.70  & 15.18  & 0.11  \\ \hline
{\color[HTML]{6200C9} Homeware}   & 1.23 & 5.15  & 0.24 & -0.07 & 3.72  & -0.018  & -0.86  & 5.15 & -0.17 \\ \hline
{\color[HTML]{00D2CB} Household tools} & 0.26  & 8.78  & 0.03 & -0.21 & 6.36  & -0.03   & 0.14  & 8.79  & 0.97  \\ \hline
{\color[HTML]{FFC9FD} Games}             & 3.26 & 16.55 & 0.20 & 1.12 &  11.98  & 0.09 & 1.37 &  16.56 & 0.08

@@

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for redundancy funds (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for a placebo timings as showed in Fig.  \ref{DID_subsidies_placebo}
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{4} $&   $ SE_{\delta_{4}}$   & t      & $\delta_{4} $ & $SE_{\delta_{4}$ & t      &  $\delta_{5}$ & $SE_{\delta_{5}}$  & t     \\ \hline
{\color[HTML]{343434} Total}        & -48   & 163    &  -0.30  & -47   & 163   & -0.29 & -47  & 163    & -0.29 \\ \hline
{\color[HTML]{343434} Manufacture}  & -34   & 114    &  -0.30  & -35   & 114   & -0.30 & -34  & 114     & -0.30   \\ \hline
{\color[HTML]{343434} Trade}        & -1.2   & 3  & -0.31  & -0.9   & 3.7  & -0.23 & -0.9   & 3.7  & -0.26 \\ \hline
{\color[HTML]{343434} Construction} & -8.3   & 30  &  -0.27 &  -7.4    & 30  & -2.44 & -8.10    & 30 & -2.67 \\ \hline
\label{sub_DID_placebo}
\end{tabular}
\end{table}
\end{landscape}
